Birbals zoete antwoord&
Birbal's Sweet Reply &
Birbal'ın Tatlı Cevap
\\
Op een dag verraste keizer Akbar zijn hovelingen met een vreemde vraag.&
One day the Emperor Akbar startled his courtiers with a strange question. &
Bir gün İmparator Akbar, sarayda garip bir soru ile ürküyordu.
\\
`Als iemand aan mijn snorharen trekt, wat voor soort straf zou hij moeten krijgen?', vroeg hij.&
"If somebody pulled my whiskers what sort of punishment should be given to him?" he asked. &
"Birisi bıyıklarımı çektiğinde ona ne tür ceza verilmeli?" O sordu.
\\
`Hij zou gegeseld moeten worden!' zei een hoveling.&
"He should be flogged!" said one courtier. &
"O avlanır!" bir saraydan biri dedi.
\\
`Hij zou opgehangen moeten worden!' zei een ander.&
"He should be hanged!" said another. &
"Asmak gerekir!" dedi başka.
\\
`Hij zou onthoofd moeten worden!' zei een derde.&
"He should be beheaded!" said a third. &
"Kafadan çekilmeli!" dedi bir üçüncü.
\\
`En wat vind jij, Birbal?' vroeg de keizer. `Wat denk jij dat gedaan zou moeten worden als iemand aan mijn snorharen trekt?'&
"And what about you, Birbal?" asked the emperor. "What do you think would be the right thing to do if somebody pulled my whiskers?" &
"Peki ya sen, Birbal?" diye sordu imparator. "Birileri bıyıklarımı çektiğinde doğru olan ne olurdu sizce?"
\\
`Hij zou snoep moeten krijgen', zei Birbal.&
"He should be given sweets," said Birbal. &
"Tatlı verilmeli," dedi Birbal.
\\
`Snoep?'; de andere hovelingen hapten naar adem.&
"Sweets?", gasped the other couriers. &
"Tatlılar mı?", Diğer kuryeleri soluk soluyordu.
\\
`Ja,' zei Birbal, `snoep, omdat de enige die aan 's majesteits snorharen durft te trekken zijn kleinzoon is.'&
"Yes", said Birbal. “Sweets, because the only one who would dare pull His Majesty's whiskers is his grandson." &
"Evet" dedi Birbal. "Tatlılar, çünkü Majesteleri nin bıyıklarını çekmeye cesaret edebilecek tek kişi torunudır."
\\
De keizer was zo ingenomen met het antwoord dat hij zijn ring af deed en  aan Birbal gaf als beloningx.&
So pleased was the emperor with the answer that he pulled off his ring and gave it to Birbal as a reward. &
İmparator, yüzüğünü çıkardığı ve Birbal'e ödül olarak vermesinden memnun oldu.
\\