Birbal is kortaf&
 Birbal Is Brief&
Birbal Kısa Özette
\\
Op een dag vroeg Akbar zijn hovelingen of zij hem het verschil tussen waarheid en leugen konden vertellen in drie woorden of minder.&
One day Akbar asked his courtiers if they could tell him the difference between truth and falsehood in three words or less.&
Bir gün Akbar, saraylarına gerçeğe ve sahtelik arasındaki farkı üç kelimeden daha az mı söyleyebileceklerini sordu.
\\
De hovelingen keken elkaar verbijsterd aan.&
The courtiers looked at one another in bewilderment.&
Saraylar şaşkınlık içinde birbirlerine baktılar.
\\
"Hoe denk jij ervan, Birbal?"&
"What about you, Birbal?"&
"Ya sen, Birbal?"
\\
vroeg de keizer.&
asked the emperor.&
diye sordu imparator.
\\
"Ik ben verrast dat jij ook stil bent."&
"I'm surprised that you too are silent."&
"Ben de sessizim sizi şaşırttı."
\\
"Ik ben stil omdat ik anderen de kans wil geven te spreken," zei Birbal.&
"I'm silent because I want to give others a chance to speak," said Birbal.&
"Ben sessizim, çünkü başkalarına konuşma şansı vermek istiyorum" dedi Birbal.
\\
"Niemand anders heeft het antwoord," zei de keizer.&
"Nobody else has the answer," said the emperor.&
"Kimsenin cevabı yok" dedi imparator.
\\
"Dus ga je gang en vertel me wat het verschil is tussen waarheid en onwaarheid -- in drie woorden of minder."&
"So go ahead and tell me what the difference between truth and falsehood is -- in three words or less."&
"Öyleyse devam edin ve bana gerçeğin ve sahte arasındaki farkın ne olduğunu söyleyin - üç kelimeden az."
\\
"Vier vingers" zei Birbal.&
"Four fingers" said Birbal.&
"Dört parmak" dedi Birbal.
\\
"Vier vingers?" vroeg de keizer, verbijsterd.&
"Four fingers?" asked the emperor, perplexed.&
"Dört parmak mı?" diye sordu imparator, şaşkın.
\\
"Dat is het verschil tussen waarheid en leugen, Majesteit," zei Birbal.&
"That's the difference between truth and falsehood, your Majesty," said Birbal.&
Birbal, "Hakikat ve sahtelik arasındaki fark bu, Majesteleri" dedi.
\\
"Dat wat je met je eigen ogen ziet, is de waarheid.&
"That which you see with your own eyes is the truth.&
"Kendi gözlerinizle gördüğünüz şey gerçektir.
\\
Dat waarvan je alleen maar gehoord hebt, is misschien niet waar.&
That which you have only heard about might not be true.&
Sadece duyduğunuz şey doğru olmayabilir.
\\
Eigenlijk, vaker wel dan niet, is het onjuist."&
In fact, more often than not, it's to be false."&
Aslında, daha sık olmasın, yanlış olur. "
\\
"Dat klopt," zei Akbar.&
"That is right," said Akbar.&
"Doğru," dedi Akbar.
\\
"Maar wat bedoelde je te zeggen dat het verschil vier vingers is?"&
"But what did you mean by saying the difference is four fingers?'&
"Ama fark dört parmağı olduğunu söyleyerek ne demek istediniz?"
\\
'De afstand tussen je ogen en je oren is de breedte van vier vingers, majesteit,' zei Birbal grijnzend.&
"The distance between one's eyes and one's ears is the width of four fingers, Your Majesty," said Birbal, grinning.&
"Bir gözüyle bir kulağınız arasındaki mesafe dört parmağınızın genişliğidir, Majesteleri." Birbal, sırıtarak.
\\