Birbal de bediende&
Birbal the Servant.&
Hizmetçi Birbal.
\\
Op een dag reden Akbar en Birbal door het landschap en kwamen toevallig langs een koolveld.&
One day Akbar and Birbal were riding through the countryside and they happened to pass by a cabbage patch.&
Bir gün Akbar ve Birbal kırsal alana biniyorlardı ve lahana tabancasından geçtiler.
\\
"Kool is zulk een heerlijke groente!" zei Akbar.&
"Cabbages are such delightful vegetables!" said Akbar.&
"Lahana çok güzel sebzeler!" dedi Akbar.
\\
"Ik hou gewoon van kool."&
"I just love cabbage."&
"Sadece lahana severim."
\\
"Kool is de koning onder de groenten!" zei Birbal.&
"The cabbage is king of vegetables!" said Birbal.&
"Lahana sebze kralı!" dedi Birbal.
\\
Een paar weken later reden ze opnieuw langs het koolveld.&
A few weeks later they were riding past the cabbage patch again.&
Birkaç hafta sonra tekrar lahana kuşağına biniyorlardı.
\\
Deze keer maakte de keizer een gezicht toen hij de groenten zag.&
This time however, the emperor made a face when he saw the vegetables.&
Ancak bu kez, imparator sebzeleri gördüğünde yüz çevirdi.
\\
"Ik hield altijd van kool, maar nu heb ik er geen zin in." zei Akbar.&
"I used to love cabbage but now I have no taste for it." said Akbar.&
"Lahana severdim ama şimdi bunun tadına bakmam." dedi Akbar.
\\
"De kool is een smakeloze groente" stemde Birbal in.&
"The cabbage is a tasteless vegetable" agreed Birbal.&
"Lahana tatsız bir sebze" Birbal'a razı oldu.
\\
De keizer was erg verbaasd.&
The emperor was astonished.&
İmparator şaşırmıştı.
\\
"Maar de laatste keer dat je zei dat het de koning onder de groenten was!"&
"But the last time you said it was the king of vegetables!"&
"Ama en son sebzenin kralı olduğunu söylemiştin!"
\\
"Dat zei ik," gaf Birbal toe, "Maar ik ben uw dienaar, Majesteit, niet die van de kool."&
"I did," admitted Birbal, "But I am your servant, Your Majesty, not the cabbage's."&
Birbal, "Ben yaptım," dedi, "Fakat ben senin hizmetkârın Majesteleri, lahana değilim" dedi.
\\